### 2018-03-26 tex/paper.tex
Add some references

\sjtnote{References to some of the background work still to be added.}

@@

One approach to this is to choose mechanisms such as bitcoin script which are manifestly non-Turing complete. A bitcoin script, written in a Forth-like language, is essentially linear: it can branch, but the language contains neither looping constructs nor recursion. It is therefore straightforward not only to see that scripts will terminate, but also to give an accurate estimate of the time taken to execute a script.

@@

On the other hand, the Ethereum system provides a Turing-complete language for the EVM virtual machine, and a higher-level programming language, Solidity, that compiles into EVM code. However, EVM and Solidity programs are constrained \emph{post hoc} by two mechanisms: program execution must be paid for using `gas' proportional to the effort expended, and a set of \emph{ad hoc} limits on program execution, e.g.\ on stack size.

@@

Programmability of the system is provided through a ``fat'' high-level API, which is accessible from Nxt clients through a REST interface. The API provides functionality supporting various kinds of transactions. The core software itself doesn't support any form of scripting language; rather, users are expected to work with the built in transaction types and transactions that support some 250 primitive operations; these can be ``scripted'' in a client (only) using a binding to the API, which is available, for instance, in JavaScript.

@@

The \ae{}ternity system~\cite{aeternity} provides multiple languages and VMs:\footnote{As presented by Erik Stenman at CODE BEAM SF, March 2018, \url{https://www.youtube.com/watch?v=VXsqvfPIdWg}} the functional language  Sophia (akin to Reason) and the Functional Typed Warded Virtual Machine (FTWVM) for safe ``system level programming'', the language Varna and the HLM for simple contracts, and a (port of) Solidity and the EVM for compatibility with Ethereum. In a similar way, Cardano provides support for IELE~\sjtnote{citation}, a rational reconstruction of the EVM, and thus for Solidity contracts too.

@@

Some chains have a layered design, in particular Cardano~\cite{cardano}. The Cardano Settlement Layer (SL) is to support settlement of transactions but nothing more complicated, whereas the Computation Layer (or CL) supports more powerful general computations over the chain. Moreover, the Cardano roadmap \cite{cardano-rationale} envisages the possibility of computation taking place, in part at least, on a sidechain rather than on the main chain itself, which may support only the SL. Other off-chain approaches include the Lightning network, overlaid on blockchains (usually Bitcoin) and the channels of \ae{}ternity, introduced below.

@@

The tool has been mainly written in Haskell and compiled to JavaScript
by the Haste compiler \cite{Haste}, it also relies on
the Blockly library \cite{Blockly} for providing a visual
editor for smart contracts written in Marlowe. Blockly's editor allows
the user to visualise and edit smart-contracts as interlocking blocks
that can be dragged and dropped like pieces of a jigsaw puzzle (see
Figure~\ref{fig:detail-of-block}). The tool also provides functionality
to generate syntactically correct and formatted code (that is displayed
in the upper right corner of the application), and to convert the
code back to its block representation.

@@

We have examined a single kind of commitment, namely a commitment of a certain amount of currency. In different 
applications, such as on-chain game playing of games like poker, a commitment to a value will be required. A value 
commitment would include a choice of a play in a game, which would be chosen and concealed from the other players until 
a later point in play, when it can be revealed. The paper \cite{kumaresan2015use} makes use of this and other 
cryptographic primitives to enforce the rules of poker while maintaining the cards of each player secret.

@@

Haskell is a pure functional programming language, and uses the \haskellinline{Monad} type class to encapsulate
operations that can potentially have a side effect. Many introductions to monads exist \sjtnote{cite some} but for the 
sake of this discussion it is enough to think of a value of type \haskellinline{m a} where \haskellinline{m} is a monad 
as a ``computation that results in something of type \haskellinline{a}''. The \haskellinline{Monad} API allows 
such computations to be assembled, and then, once assembled, they may be run, in general causing some side-effects as a 
part of the computation.

>>>>

@@

One approach to this is to choose mechanisms such as bitcoin script~\cite{BitcoinWikiScript} which are manifestly 
non-Turing complete. A bitcoin script, written in a Forth-like language, is essentially linear: it can branch, but the 
language contains neither looping constructs nor recursion. It is therefore straightforward not only to see that scripts 
will terminate, but also to give an accurate estimate of the time taken to execute a script.

@@

On the other hand, the Ethereum system~\cite{wood2014ethereum} provides a Turing-complete language for the EVM virtual 
machine, and a higher-level programming language, Solidity, that compiles into EVM code. However, EVM and Solidity 
programs are constrained \emph{post hoc} by two mechanisms: program execution must be paid for using `gas' proportional 
to the effort expended, and a set of \emph{ad hoc} limits on program execution, e.g.\ on stack size.

@@

In Nxt~\cite{Nxt}, programmability of the system is provided through a ``fat'' high-level 
API, which is accessible from Nxt clients through a REST interface. The API provides functionality supporting various 
kinds of transactions. The core software itself doesn't support any form of scripting language; rather, users are 
expected to work with the built in transaction types and transactions that support some 250 primitive operations; these 
can be ``scripted'' in a client (only) using a binding to the API, which is available, for instance, in JavaScript.

@@

The \ae{}ternity system~\cite{aeternity} provides multiple languages and VMs:\footnote{As presented by Erik Stenman at CODE BEAM SF, March 2018, \url{https://www.youtube.com/watch?v=VXsqvfPIdWg}} the functional language  Sophia (akin to Reason) and the Functional Typed Warded Virtual Machine (FTWVM) for safe ``system level programming'', the language Varna and the HLM for simple contracts, and a (port of) Solidity and the EVM for compatibility with Ethereum. In a similar way, Cardano provides support for IELE~\cite{IELE}, a rational reconstruction of the EVM, and thus for Solidity contracts too.

@@

Some chains have a layered design, in particular Cardano~\cite{cardano}. The Cardano Settlement Layer (SL) is to support settlement of transactions but nothing more complicated, whereas the Computation Layer (or CL) supports more powerful general computations over the chain. Moreover, the Cardano roadmap~\cite{cardano-rationale} envisages the possibility of computation taking place, in part at least, on a sidechain rather than on the main chain itself, which may support only the SL. Other off-chain approaches include the Lightning network, overlaid on blockchains (usually Bitcoin) and the channels of \ae{}ternity, introduced below.

@@

The tool has been mainly written in Haskell and compiled to JavaScript
by the Haste compiler~\cite{Haste}, it also relies on
the Blockly library~\cite{Blockly} for providing a visual
editor for smart contracts written in Marlowe. Blockly's editor allows
the user to visualise and edit smart-contracts as interlocking blocks
that can be dragged and dropped like pieces of a jigsaw puzzle (see
Figure~\ref{fig:detail-of-block}). The tool also provides functionality
to generate syntactically correct and formatted code (that is displayed
in the upper right corner of the application), and to convert the
code back to its block representation.

@@

We have examined a single kind of commitment, namely a commitment of a certain amount of currency. In different 
applications, such as on-chain game playing of games like poker, a commitment to a value will be required. A value 
commitment would include a choice of a play in a game, which would be chosen and concealed from the other players until 
a later point in play, when it can be revealed. The paper~\cite{kumaresan2015use} makes use of this and other 
cryptographic primitives to enforce the rules of poker while maintaining the cards of each player secret.

@@

Haskell is a pure functional programming language, and uses the \haskellinline{Monad} type class to encapsulate
operations that can potentially have a side effect. Many introductions to monads exist \cite{wadler1990comprehending} 
but for the sake of this discussion it is enough to think of a value of type \haskellinline{m a} where \haskellinline{m} 
is a monad as a ``computation that results in something of type \haskellinline{a}''. The \haskellinline{Monad} API 
allows such computations to be assembled, and then, once assembled, they may be run, in general causing some 
side-effects as a part of the computation.
